---
title: "p8105_hw1_lq2234"
author: "Lu Qiu"
date: "2023-09-16"
output: html_document
---

### Problem 1

Load the packages:
```{r, echo=TRUE, message=FALSE}
library(moderndive)
library(ggplot2)
```

Load the `early_january_weather` dataset:

```{r}
data("early_january_weather")
```
Here is a short description of the dataset using inline R code:

* This dataset contains `r ncol(early_january_weather)` variables, which are:  `r names(early_january_weather)`.  
* This dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.  
* The mean temperature is: `r round(mean(early_january_weather$temp), digit =2)`.

Make a scatterplot of `temp` (y) vs `time_hour` (x):

```{r fig.height = 4, fig.width = 14}
ggplot(early_january_weather, aes(x = time_hour, y = temp)) + geom_point(aes(colour=humid)) + scale_x_datetime(date_breaks = "1 day")
```
Patterns that are apparent in this plot:

* The temperature shows an increasing trend from 2013-01-01 to 2013-01-15.  
* Within a single day, the temperature is highest at noon and lower during the morning and night.
* Within a single day, the humidity is highest at night.
* The overall humidity is high from 2013-01-12 to 2013-01-15.

Export the scatterplot to the project directory using ggsave:
```{r fig.height = 4, fig.width = 14, message=FALSE}
ggsave("temp_time_scatter.png")
```



### Problem 2

