---
title: "p8105_hw1_lq2234"
author: "Lu Qiu"
date: "2023-09-16"
output: html_document
---

### Problem 1

Load the packages:
```{r, echo=TRUE, message=FALSE}
library(moderndive)
library(ggplot2)
library(tidyverse)
```

Load the `early_january_weather` dataset:

```{r}
data("early_january_weather")
```
Here is a short description of the dataset using inline R code:

* This dataset contains `r ncol(early_january_weather)` variables, which are:  `r names(early_january_weather)`.  
* This dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.  
* The mean temperature is: `r round(mean(early_january_weather$temp), digit =2)`.

Make a scatterplot of `temp` (y) vs `time_hour` (x):

```{r fig.height = 4, fig.width = 14}
ggplot(early_january_weather, aes(x = time_hour, y = temp)) + geom_point(aes(colour=humid)) + scale_x_datetime(date_breaks = "1 day")
```
Patterns that are apparent in this plot:

* The temperature shows an increasing trend from 2013-01-01 to 2013-01-15.  
* Within a single day, the temperature is highest at noon and lower during the morning and night.
* Within a single day, the humidity is highest at night.
* The overall humidity is high from 2013-01-12 to 2013-01-15.

Export the scatterplot to the project directory using ggsave:
```{r fig.height = 4, fig.width = 14, message=FALSE}
ggsave("temp_time_scatter.png")
```


### Problem 2

Create a data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”


```{r}
random_sample <- rnorm(10)
logical_vector <- random_sample > 0
character_vector <- c("Male", "Female", "Female", "Male", "Female", "Female", "Male", "Male", "Male", "Female")
factor_vector <- factor(rep(1:3, len = 10))
df <- data.frame(random_sample,
                 logical_vector,
                 character_vector,
                 factor_vector)
print(df)
```
The mean of the `random_sample` is `r mean(pull(df,1))`.  
The mean of the `logical_vector` is `r mean(pull(df,2))`.  
The mean of the `character_vector` is `r mean(pull(df,3))`.  
The mean of the `factor_sample` is `r mean(pull(df,4))`.

The mean of `random_sample` and `logical_vector`can be calculated, while the mean of `character_vector` and `factor_sample` cannot be calculated.

```{r, warning=FALSE, results='hide'}
as.numeric(pull(df,2))
as.numeric(pull(df,3))
as.numeric(pull(df,4))
```

What happens, and why?

* Applying as.numeric to a logical vector converts it to a numeric vector where TRUE becomes 1 and FALSE becomes 0. This conversion helps explain what happens when trying to take the mean. Because the mean of a numeric vector containing 0s and 1s makes sense, the logical vector is coerced to a numeric vector when using mean().
* Applying as.numeric to a character vector does not provide meaningful results because characters cannot be directly converted to numeric values. R converts each character to NA, and taking the mean of NA values will result in NA.  
* Applying as.numeric to a factor vector converts the factor levels to their underlying integer representation. Taking the mean of these integers does not have a meaningful interpretation, so the mean is also NA.



